Practice Problems

### 2023-10-04 Lahman Analysis/Rough Analysis/RoughAnalysis.qmd
Got stan set up

@@

>>>>

Of course, we don't want to analyze all data from 1871-present since the game has changed considerable since then. So filter to only consider seasons past WW2 (1945). We can always cut down from here, but this will give us a huge sample to use where the rules (nor the game) has changed significantly since.

```{r}
Modern.Batting <- Batting %>% 
  filter(yearID > 1945)
```

@@

# Ulam

### 2023-10-04 Stats Rethinking/Ch9/Practice Problems.qmd
Got stan set up

>>>>

Re-estimate the terrain ruggedness model from the chapter but now use a uniform prior for the standard deviation, `sigma`. The uniform prior should be `dunif(0,1)`. Use `ulam` to estimate the posterior. Does the different prior have any detectable influence on the posterior distribution of `sigma`? Why or why not?

```{r}
#Set up for model
data("rugged")
d <- rugged
d$log_gdp <- log(d$rgdppc_2000)
dd <- d[complete.cases(d$rgdppc_2000),]
dd$log_gdp_std <- dd$log_gdp / mean(dd$log_gdp)
dd$rugged_std <- dd$rugged / max(dd$rugged)
dd$cid <- ifelse(dd$cont_africa==1, 1, 2)

dat_slim <- list(
  log_gdp_std = dd$log_gdp_std,
  rugged_std = dd$rugged_std,
  cid = as.integer(dd$cid)
)

#Run model
m9.1 <- ulam(
  alist(
    log_gdp_std ~ dnorm(mu, sigma),
    mu <- a[cid] + b[cid]*(rugged_std - 0.215),
    a[cid] ~ dnorm(1, 0.1),
    b[cid] ~ dnorm(0, 0.3),
    sigma ~ dexp(1)
  ), data=dat_slim, chains=1
)
```

```{r}
#Let's examine down here so we don't rerun that process a ton, it took a LONG time
precis(m9.1, depth=2)
```

```{r}
#Now we can do the problem
m9M1 <- ulam(
  alist(
    log_gdp_std ~ dnorm(mu, sigma),
    mu <- a[cid] + b[cid]*(rugged_std - 0.215),
    a[cid] ~ dnorm(1, 0.1),
    b[cid] ~ dnorm(0, 0.3),
    sigma ~ dunif(0,1)
  ), data=dat_slim, chains=1
)
```

```{r}
precis(m9M1, depth=2)
```

# 9M2

Modify the terrain ruggedness model again. This time, change the prior for `b[cid]` to `dexp(0.3)`. What does this do to the posterior distribution? Can you explain it?

# 9M3

Re-estimate one of the Stan models from the chapter, but at different number of `warmup iterations`. Be sure to use the same number of sampling iterations in each case. Compare the `n_eff` values. How much warm-up is enough?

# 9H1

# 9H2

# 9H3

# 9H4

# 9H5

# 9H6

# 9H7
